Spatial Reasoning and Statistical Graphics

### 2014-10-11 Paper/Draft1/TestingVisualAptitude.Rnw
Art association modification

Actually, they were split up like that because of continuous vs. categorical. It's not easy to facet when you have different $x$ scales. I've removed video games entirely for the time being. 
}
Results are presented graphically in figures \ref{fig:visualaptitudects} and \ref{fig:visualaptitudecat}.

>>>>

Actually, they were split up like that because of continuous vs. categorical. It's not easy to facet when you have different $x$ scales. I've removed video games entirely for the time being. 
}

\comment{What happened to the arts skills? I seem to have a positive association now - why is my data different from yours? \\
I have the same updated results you do. I see that Stephanie changed the data file (but didn't add any more rows)... is it possible something changed there? Otherwise, maybe my dropbox didn't update correctly the first time?}
Results are presented graphically in figures \ref{fig:visualaptitudects} and \ref{fig:visualaptitudecat}.
